Constructing the transition graphs of interacting hysterons

### 2022-05-30 Paper_draft.tex
Reworked introduction to section on constructing graphs

We here establish a method for finding the transition graphs that are possible for coupled hysterons. Rather than constructing the coupled transition graph from scratch, we start from a Preisach graph, then add the coupling effects of scrambling and avalanches one by one.\\
\subsection{Candidate graphs}

@@

\subsection{Realizability}

>>>>

We here establish a method for finding the transition graphs that are possible for coupled hysterons. We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$. Next, in section \ref{ssec:realizability}, we explain how to evaluate whether or not a graph is realizable by checking whether its underlying design inequalities have a solution. Finally, we improve on the candidate graph method by introducing the concept of base graphs. 
\subsection{Candidate graphs}\label{ssec:candidate_graphs}

@@

\subsection{Realizability}\label{ssec:realizability}
